---
title: Getting and Cleaning Data Course Project
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(ggplot2)
library(dplyr)
library(xtable)
library(readr)
setwd("~/Escritorio/tareas en R")
```

uploading files hosted on my computer

```{r,echo=TRUE,results='asis'}
features <- read.table("/home/yeferson/Escritorio/tareas en R/UCI HAR Dataset/features.txt", col.names = c("n","functions"))
activities <- read.table( "/home/yeferson/Escritorio/tareas en R/UCI HAR Dataset/activity_labels.txt", col.names = c("code", "activity"))
subject_test <- read.table("/home/yeferson/Escritorio/tareas en R/UCI HAR Dataset/test/subject_test.txt", col.names = "subject")
x_test <- read.table("/home/yeferson/Escritorio/tareas en R/UCI HAR Dataset/test/X_test.txt", col.names = features$functions)
y_test <- read.table("/home/yeferson/Escritorio/tareas en R/UCI HAR Dataset/test/y_test.txt", col.names = "code")
subject_train <- read.table("/home/yeferson/Escritorio/tareas en R/UCI HAR Dataset/train/subject_train.txt", col.names = "subject")
x_train <- read.table("/home/yeferson/Escritorio/tareas en R/UCI HAR Dataset/train/X_train.txt", col.names = features$functions)
y_train <- read.table("/home/yeferson/Escritorio/tareas en R/UCI HAR Dataset/train/y_train.txt", col.names = "code")

```

First, the training and test sets are merged to create a data set.

```{r,echo=TRUE,results='asis'}
X <- rbind(x_train, x_test)
Y <- rbind(y_train, y_test)
Subject <- rbind(subject_train, subject_test)
Merged_Data <- cbind(Subject, Y, X)
```



Step 2: Extracts only the measurements on the mean and standard deviation for each measurement.


```{r,echo=TRUE,results='asis'}
TidyData <- Merged_Data %>% select(subject, code, contains("mean"), contains("std"))
```



Step 3: Uses descriptive activity names to name the activities in the data set.

```{r,echo=TRUE,results='asis'}
TidyData$code <- activities[TidyData$code, 2]
```

Step 4: Appropriately labels the data set with descriptive variable names.
```{r,echo=TRUE,results='asis'}
names(TidyData)[2] = "activity"
names(TidyData)<-gsub("Acc", "Accelerometer", names(TidyData))
names(TidyData)<-gsub("Gyro", "Gyroscope", names(TidyData))
names(TidyData)<-gsub("BodyBody", "Body", names(TidyData))
names(TidyData)<-gsub("Mag", "Magnitude", names(TidyData))
names(TidyData)<-gsub("^t", "Time", names(TidyData))
names(TidyData)<-gsub("^f", "Frequency", names(TidyData))
names(TidyData)<-gsub("tBody", "TimeBody", names(TidyData))
names(TidyData)<-gsub("-mean()", "Mean", names(TidyData), ignore.case = TRUE)
names(TidyData)<-gsub("-std()", "STD", names(TidyData), ignore.case = TRUE)
names(TidyData)<-gsub("-freq()", "Frequency", names(TidyData), ignore.case = TRUE)
names(TidyData)<-gsub("angle", "Angle", names(TidyData))
names(TidyData)<-gsub("gravity", "Gravity", names(TidyData))
```


Step 5: From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.
```{r,echo=TRUE,results='asis'}
FinalData <- TidyData %>%
    group_by(subject, activity) %>%
    summarise_all(funs(mean))
write.table(FinalData, "FinalData.txt", row.name=FALSE)
```

Checking variable names
```{r,echo=TRUE}
str(FinalData)
```


```{r,echo=TRUE,results='asis'}
knitr::kable(FinalData)
```

